%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nejc-ilenic}{\Large Nejc Ilenič}} \\
  LinkedIn: \href{https://www.linkedin.com/in/nejc-ilenic}{https://www.linkedin.com/in/nejc-ilenic} \\ GitHub: \href{https://github.com/inejc}{https://github.com/inejc} & Email : \href{mailto:nejc.ilenic@gmail.com}{nejc.ilenic@gmail.com} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ljubljana, Faculty of Computer and Information Science}{Ljubljana, Slovenia}
      {Master's degree, Computer Science}{2015 -- 2017}
    \resumeSubheading
      {University of Ljubljana, Faculty of Computer and Information Science}{Ljubljana, Slovenia}
      {Bachelor's degree, Computer Science}{2011 -- 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GlobalWebIndex}{London, United Kingdom}
      {Machine Learning Engineer}{Feb 2018 - April 2020}
      \resumeItemListStart
        \resumeItem{Pollpass}
          {I was working in a remote team building Pollpass, a distributed, real-time surveying platform. My responsibilities were leading the design and implementation of two key components; an outbound data pipelining / warehousing system and development of intelligent algorithms for ensuring data quality.}
      \resumeItemListEnd

    \resumeSubheading
      {Bioinformatics Laboratory, University of Ljubljana}{Ljubljana, Slovenia}
      {Software Developer}{Aug 2016 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Orange}
          {My main responsibility was to design and implement a system for simplifying the embedding process of digital images. We deployed various pre-trained convolutional neural networks to a remotely accessible service and exposed the functionality in Orange (an open-source machine learning and data visualization software available at \href{https://orange.biolab.si}{https://orange.biolab.si)}.}
      \resumeItemListEnd

    \resumeSubheading
      {4th Office}{Ljubljana, Slovenia}
      {Software Developer}{Aug 2015}
      \resumeItemListStart
        \resumeItem{Internship}
          {I attended a one-month internship where I worked on a C\# backend project. The collaboration was a result of successful participation in a student competition.}
      \resumeItemListEnd

    \resumeSubheading
      {IT klinika d.o.o}{Ljubljana, Slovenia}
      {Software Developer}{Jul 2014 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Harmonia}
          {I worked in a small team of students developing a Django project for online booking of beauty and wellness services. The collaboration was a result of successful participation in a student competition.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}

  \resumeSubHeadingListStart
    \resumeSubItem{Slovenian Tarok card game environment}
      {A C++ implementation of the Slovenian Tarok card game environment for the OpenSpiel framework.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{doddle-model: machine learning in Scala}
      {An in-memory machine learning library implemented in Scala.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{A PyTorch implementation of Paragraph Vectors}
      {A PyTorch implementation of the Distributed Representations of Sentences and Documents paper by Q. V. Le et al.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{Orange3 Image Analytics Add-on}
      {Orange3 Image Analytics is an add-on for the Orange3 data mining suite (an open-source software). It provides extensions for importing/creating labeled image data sets and embedding them through a variety of pre-trained deep neural networks.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{Educational Neural Networks Library}
      {A pure Python and NumPy implementation of a neural networks library developed for educational purposes.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{16th place solution for the Intel \& MobileODT Cervical Cancer Screening competition on Kaggle}
      {The challenge of the competition was to develop an algorithm that accurately identifies a woman’s cervix type based on digital images. Our team ended up 16th out of 848 teams on the private, final leaderboard (top 2 \%).}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{Winning Solution for the Painter by Numbers Competition on Kaggle}
      {The challenge of the competition was to examine pairs of paintings and determine whether they were painted by the same artist.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubItem{Domain Independent Monte Carlo Tree Search Methods Implementation}
      {A Java implementation of Monte Carlo Tree Search methods that is self-contained and domain-independent. The project was developed for my Bachelor’s thesis.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
